Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-13 bbbq_article.tex
Fix ref
Found which numbers are correct

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
  }
  \label{fig:elution}
\end{figure}

@@

Figure \ref{fig:elution_versus} shows the percentage of TMH-derived
epitopes as presented \emph{in vivo} in T cells. 
The data was obtained from the IEDB and includes only the MHC
alleles as used in this study. As there are many (especially class II)
MHC alleles, only a small percentage of the full IEDB data could be used.
Although this figure demonstrates that TMH-derived epitopes are presented
\emph{in vivo}, we excluded this figure from the main article, as these
protocols select epitopes in a non-random fashion (unlike the
MHC ligand assays, as presented in the main article).

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
  }
  \label{fig:t_cells_present_tmh_derived_epitopes}
\end{figure}

>>>>

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
    \richel{These numbers (and probably, due to that, the
    percentages) are incorrect}
  }
  \label{fig:elution}
\end{figure}

@@

Figure \ref{fig:t_cells_present_tmh_derived_epitopes} 
shows the percentage of TMH-derived
epitopes as presented \emph{in vivo} in T cells. 
The data was obtained from the IEDB and includes only the MHC
alleles as used in this study. As there are many (especially class II)
MHC alleles, only a small percentage of the full IEDB data could be used.
Although this figure demonstrates that TMH-derived epitopes are presented
\emph{in vivo}, we excluded this figure from the main article, as these
protocols select epitopes in a non-random fashion (unlike the
MHC ligand assays, as presented in the main article).

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
    \richel{Numbers must be approx 259 and 651}
  }
  \label{fig:t_cells_present_tmh_derived_epitopes}
\end{figure}
